---
title: "Creation of 2016 General Social Survey"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This notebook imports the full General Social Survey data release from ICPSR and creates the minimal version needed for the SOC 4015 final project.

## Dependencies
This notebook requires a number of packages:

```{r load-packages}
# tidyverse packages
library(dplyr)  # data cleaning

# other packages
library(here)   # file path management
```

## Load Data
This notebook requires the raw data to be loaded so that it can be cleaned:

```{r load-data}
load(file = here("data", "36797-0001-Data.rda"))
```

## Subset and Tidy Data
First, we want to limit the years present in our data:

```{r subset-year}
gss16 <- filter(da36797.0001, YEAR == 2016)
```

Next, we remove variables that were not measured in 2016:

```{r}
gss16 <- Filter(function(x) !(all(x=="")), gss16)
```

Then we convert the data to a tibble:

```{r}
gss16 <- as_tibble(gss16)
```

## Export Data

Finally, we expor the cleaned up data as a useable object:

```{r}
save(gss16, file = here("data", "gss16.rda"))
```
